Refinements for open automata

### 2021-08-05 2021-Refinement/paper/refinementarticle.tex
Example

\TODO{Some related work on other models than open automata introduce refinement relations.
In a chapter by Bellegarde, Julliand and Kouchnarenko \cite{10.1007/3-540-46428-X_19}, a simulation relation on transition systems is introduced.
This simulation encompass action refinement, is able to deal with silent actions and is compatible with parallel composition.
Here the refinement relation does not consider action refinement as valid but it should be done in future work.
Also they check how LTL properties are preserved or combined using their refinement which we do not do.
However their model is less expressive: the transition system model is less expressive than open automata and the parallel composition is less expressive than composition on open automata.
In a later report by Kouchnarenko and Lanoix \cite{10.1007/978-3-540-70881-0_26}, the refinement relation they introduce is on LTS (labelled transition systems).
Their relation additionally prevents deadlock and livelocks.
The composition is also extended to synchronised composition which is more expressive.
In our work we also deal with deadlocks but not with livelocks since the latter arise only with silent actions.
This work is closer than the previous one to what we do here, still open automata are more expressive than LTS and composition is more general than sychronised composition.}

@@

>>>>

\TODO{Some related work on other models than open automata introduce refinement relations.
In a chapter by Bellegarde, Julliand and Kouchnarenko \cite{10.1007/3-540-46428-X_19}, a simulation relation on transition systems is introduced.
This simulation encompass action refinement, is able to deal with silent actions and is compatible with parallel composition.
Here the refinement relation does not consider action refinement as valid but it should be done in future work.
Also they check how LTL properties are preserved or combined using their refinement which we do not do.
However their model is less expressive: the transition system model is less expressive than open automata and the parallel composition is less expressive than composition on open automata.
In a later report by Kouchnarenko and Lanoix \cite{10.1007/978-3-540-70881-0_26}, the refinement relation they introduce is on LTS (labelled transition systems).
Their relation additionally prevents deadlock and livelocks.
The composition is also extended to synchronised composition which is more expressive.
In our work we also deal with deadlocks but not with livelocks since the latter arise only with silent actions.
This work is closer than the previous one to what we do here, still open automata are more expressive than LTS and composition is more general than synchronised composition.}

@@

\begin{figure}
\centering
\input{Traffic_Lights_Interm.tex}
\caption{The incomplete Specification Traffic Lights system}
\label{fig:tlf}
\end{figure}
